---
title: "QA0 Report"
author: "PMG Group"
output:
  pdf_document:
    fig_caption: yes
    fig_crop: no
    fig_width: 8
    keep_tex: yes
    number_sections: yes
geometry: margin=0.5in
fontsize: 10pt
---

```{r echo=FALSE, message=FALSE, warning=F}
library(png)
library(gridExtra)
library(ggplot2)
library(ggthemes)
library(quantreg)
library(pander)
library(dplyr)
library(knitr)
library(locfit)
theme_set(theme_bw())

dire <- "Xa16f89_X1e17/"

antennas <- read.csv(paste(dire, 'antennas.csv', sep = ""))
caldata <- read.csv(paste(dire, 'caldata.csv', sep = ""))

atmosphere <- read.csv(paste(dire, 'atmosphere.csv', sep = ""))
atmosphere$TIME <- as.POSIXct(atmosphere$TIME, 'GMT')
atmosphere <- subset(atmosphere, tsys_X != 0 & tsys_Y != 0)
atmosphere <- 
  left_join(atmosphere,
            select(caldata, CALDATA_ID, SCAN),
            by='CALDATA_ID')

delay <- read.csv(paste(dire, 'delay.csv', sep = ""))
delay$TIME <- as.POSIXct(delay$TIME, 'GMT')

field <- read.csv(paste(dire, 'field.csv', sep = ""))
fieldsrc <- read.csv(paste(dire, 'fieldsource.csv', sep = ""))
flags <- read.csv(paste(dire, 'flags.csv', sep = ""))
focus <- read.csv(paste(dire, 'focus.csv', sep = ""))
main <- read.csv(paste(dire, 'main.csv', sep = ""))

phase <- read.csv(paste(dire, 'phase.csv', sep = ""))
phase <- 
  left_join(phase,
            select(caldata, CALDATA_ID, SCAN),
            by='CALDATA_ID')
point <- read.csv(paste(dire, 'point_qa0.csv', sep = ""))
point_trend <- read.csv(paste(dire, 'point_qa1.csv', sep = ""))

sbsum <- read.csv(paste(dire, 'sbsum.csv', sep = ""))
sbsum$RA <- sbsum$RA / 15

scan <- read.csv(paste(dire, 'scan.csv', sep = ""))
scan$START_TIME <- as.POSIXct(scan$START_TIME, 'GMT')
scan$END_TIME <- as.POSIXct(scan$END_TIME, 'GMT')

scparam <- read.csv(paste(dire, "scienceparam.csv", sep = ""))
slt <- read.csv(paste(dire, 'slt.csv', sep = ""))
subscan <- read.csv(paste(dire, 'subscans.csv', sep = ""))
subscan$START_TIME <- as.POSIXct(subscan$START_TIME, 'GMT')
subscan$END_TIME <- as.POSIXct(subscan$END_TIME, 'GMT')
subscan$delta <- difftime(subscan$END_TIME,subscan$START_TIME, units="secs")
wvr <- read.csv(paste(dire, 'wvr.csv', sep = ""))
wvr$TIME <- as.POSIXct(wvr$START_TIME, 'GMT')

calamp <- read.csv(paste(dire, 'cal_amp.csv', sep = ""))

trec_max <- data.frame(bands = c("ALMA_RB_03", "ALMA_RB_04", "ALMA_RB_06",
                                 "ALMA_RB_07", "ALMA_RB_08", "ALMA_RB_09",
                                 "ALMA_RB_10"),
                       temp = c(45 * 1.5, 82 * 1.1, 136 * 1.1,
                                219 * 1.1, 292 * 1.1, 261 * 1.1,
                                344 * 1.1))
trec_max$bands <- as.character(trec_max$bands)

deg_to_dms <- function(degfloat) {
  if (degfloat < 0) {
    neg <- TRUE
    degfloat <- -1 * degfloat
  } else {
    neg <- FALSE
  }
  degi <- as.integer(degfloat)
  deg <- sprintf("%02d", degi)
  minfloat <- 60 * (degfloat - degi)
  mini <- as.integer(minfloat)
  min <- sprintf("%02d", mini)
  secfloat <- 60 * (minfloat - mini)
  secfloat <- sprintf("%05.2f", secfloat)
  if (neg) {
    deg <- paste("-", deg, sep="")
  }
  
  dm <- paste(deg, min, sep=":")
  dms <- paste(dm, secfloat, sep=":")
  return (dms)
}
```

# EB, SB and Array Information

```{r warning=FALSE, echo=FALSE, message=FALSE}
names(slt) <- 
  c("EB UID:", "Start Time:", "Number of Scans:", "EB Status:", "SB UID:",
    "SB Name:",  "Project Code:", "Array Name:", "Array Family:", 
    "Correlator:", "SE_ID", "SE_SUBJECT")

kable(t(slt[,c(-11,-12)]),
      col.names = c('Value'),
      align ='r',
      caption = "Execution Block Information.",
      booktabs = TRUE)

sbsumt <- select(
  sbsum, SB_UID, sbName, CODE, band, repfreq, RA, DEC, 
  minArrayAR100GHz, maxArrayAR100GHz, AR100GHz, LAS100GHz, bestconf)

names(sbsumt) <- c(
  "SB UID:", "SB Name:", "Project Code:", "Band:", "Representtive Freq.:", 
  "RA:", "DEC:", "Min. Array AR (100GHz):", "Max. Array AR (100GHz):", 
  "SB req. AR (100GHz):", "SB req. LAS (100GHz):", "Best Configuration:")

tsbsumt <- t(sbsumt)
tsbsumt[5,1] <- paste(format(as.numeric(tsbsumt[5,1]), digits=2, nsmall=2),
                      "GHz.")
tsbsumt[6,1] <- deg_to_dms(as.numeric(tsbsumt[6,1]))
tsbsumt[7,1] <- deg_to_dms(as.numeric(tsbsumt[7,1]))
tsbsumt[8,1] <- paste(format(as.numeric(tsbsumt[8,1]), digits=2, nsmall=2),
                      "arcsec.")
tsbsumt[9,1] <- paste(format(as.numeric(tsbsumt[9,1]), digits=2, nsmall=2),
                      "arcsec.")
tsbsumt[10,1] <- paste(format(as.numeric(tsbsumt[10,1]), digits=2, nsmall=2),
                      "arcsec.")
tsbsumt[11,1] <- paste(format(as.numeric(tsbsumt[11,1]), digits=2, nsmall=2),
                      "arcsec.")

kable(tsbsumt,
  col.names = c('Value'),
  align ='r',
  caption = "Scheduling Block Information.",
  digits = 1
  )

# EB Execution Time
ttot <- difftime(max(scan$END_TIME), min(scan$START_TIME), units='mins')

target_scan <- scan %>% subset(SCAN_INTENT == "OBSERVE_TARGET") 
target_subscan <- subscan %>% subset(SCAN %in% target_scan$SCAN & INTENT == "ON_SOURCE")

time_on_source <- sum(target_subscan$delta)


```

Num Antennas: `r length(antennas$ANTENNA)`.

Total Execution Time: `r format(ttot, digits = 3, nsmall=1)`.

EB Integration Time on Source: `r format(as.numeric(time_on_source, units="mins"), digits = 3, nsmall=1)` mins.

SB Requested Time on Source: `r format(nrow(fieldsrc) * scparam$intTime / 60, digits = 3, nsmall = 1)` mins.

Is Polarization? `r ifelse(as.logical(sbsum$isPolarization[1]) == TRUE, "True", "False")`.


# QA0 Summary

## Check Flagged Data

```{r flags, warning=FALSE, echo=FALSE, message=FALSE, results='asis'}
# Summary of flags
flags <- left_join(flags, select(antennas, ANTENNA_ID, ANTENNA), by='ANTENNA_ID')

flag_sum <- 
  flags %>%
  group_by(ANTENNA) %>% 
  summarise(flags = n(), total = sum(delta) / 60.)



# Creating a list of antennas with more than 10% of the data flagged
# Maybe better to use the median to set limit? % is missleading with small ttot
antenna_flag <- 
  as.character(subset(flag_sum, total > 0.15 * as.numeric(ttot))$ANTENNA)

flag_high <- subset(flag_sum, total > 0.15 * as.numeric(ttot))

if (length(antenna_flag) > 0) {
  kable(subset(flags, ANTENNA %in% antenna_flag) %>% 
          group_by(ANTENNA, REASON) %>% 
          summarise(Tot = sum(delta) / 60.) %>%
          arrange(-Tot),
        digits = 2)
} else {
  cat("No antennas with more than 10% of data flagged.")
}
```

## Check Calibration Intents

```{r warning=FALSE, echo=FALSE, message=FALSE, results='asis'}
qaflag <- "Pass"
calint <- scan %>% group_by(SCAN_INTENT) %>% summarise(scanNum = n())

intents <- c("CALIBRATE_BANDPASS", "CALIBRATE_SIDEBAND_RATIO",
             "CALIBRATE_POINTING", "CALIBRATE_AMPLI", "CALIBRATE_PHASE")

if (!"OBSERVE_TARGET" %in% calint$SCAN_INTENT) {
  cat("No time on Source! Fail QA0.")
  qaflag <- "FAIL"
}

for (i in intents) {
  if (i %in% calint$SCAN_INTENT) {
    next
  }
  else {
    cat("The following Intent is missing: ", i)
    qaflag <- "Pass"
    break
  }
}

cat(qaflag)
```

## Check Mosaic Coverage / Pointings

```{r warning=FALSE, echo=FALSE, message=FALSE, results='asis'}
qaflag <- "Pass"
field_tar <- as.character(unique(target_subscan$FIELD_NAME))

for (f in field_tar) {
  field_sel <- field %>% subset(FIELD_NAME == f)
  field_sscan <- target_subscan %>% subset(FIELD_NAME == f)
  # cat(format(nrow(field_sel) - 1), "\n")
  sb_src <- fieldsrc %>% subset(sourcename == f)
  # cat(sb_src$pointings, "\n")
  # cat(nrow(field_sscan), "\n")
  fract <- nrow(field_sscan) / sb_src$pointings
  if (fract - trunc(fract) != 0) {
    cat("There is some problem in mosaic coverage \n")
    qaflag <- "SEMIPASS"
  }
}

cat(qaflag)
```

## Check Array Resolution

## Check Atmosphere Calibrations

```{r atm, warning=FALSE, echo=FALSE, message=FALSE, results='asis'}
# Remove flagged antennas from the atmosphere table
atmclean <- atmosphere
if (length(antenna_flag) > 0) {
  atmclean <- 
    subset(atmclean,
           !as.character(ANTENNA) %in% as.character(antenna_flag))
}

# Create summary of sbgain per antenna, per BB, per polarizations
atmgain <-
  atmosphere %>%
  group_by(ANTENNA, BB) %>%
  summarise(sbgainX = median(sbgain_X), sbgainY = median(sbgain_Y))

# Detect sbgain outliers
if (as.character(sbsum[1, 'band']) != "ALMA_RB_09") {
  outgain <- subset(atmgain, sbgainX < 0.9 | sbgainY < 0.9)
} else {
  outgain <- subset(atmgain, (sbgainX < 0.3 | sbgainX > 0.7) | 
                      (sbgainY < 0.3 | sbgainY > 0.7))
}

# Any antenna with outliers is removed from further analysis
if (nrow(outgain) > 0) {
  atmclean <- 
    subset(atmclean,
           !as.character(ANTENNA) %in% as.character(outgain$ANTENNA))
  cat("Antenna(s)", as.character(unique(outgain$ANTENNA)), "have SBgain outside spec (see details).")
}

# First atmosphere summary, fot remove bad scans
atmsum1 <-
  atmclean %>%
  group_by(SCAN, BB) %>% 
  summarise(trecX = median(trec_X), trecY = median(trec_Y), 
            tsysX = median(tsys_X), tsysY = median(tsys_Y))
# limit temperatured for Trec
tlim <- trec_max[
  as.character(trec_max$bands) == as.character(sbsum[1, 'band']),
  2]

# Create list of Scans with issues
atmscan_bad <-
  atmsum1 %>%
  subset(trecX < 0 | trecY < 0 | tsysX < 0 | tsysY < 0 |
         trecX > tlim | trecY > tlim | tsysX > 5e3 | tsysY > 5e3)

# Any missing atmosphere scan reduced?

check_sa <- 
  scan[scan$SCAN_INTENT == "CALIBRATE_ATMOSPHERE", 'SCAN'] %in% 
  caldata[caldata$CAL_INTENT == "CAL_ATMOSPHERE", 'SCAN']

if (FALSE %in% check_sa) {
  cat("Missing at least one Telcal online reduction. Semipass?\n")
}

# Remove bad Scans from further analysis
if (nrow(atmscan_bad) > 0) {
  atmclean <-
    subset(atmclean, !as.character(SCAN) %in% as.character(atmscan_bad$SCAN))
}

# Detect antennas with gross temperature problems
atmant_bad <- 
  atmclean %>% 
  subset(tsys_X < 0 | tsys_Y < 0 | trec_X < 0 | trec_Y < 0 |
         trec_X > tlim | trec_Y > tlim | tsys_X > 5e3 | tsys_Y > 5e3,
         select = c(ANTENNA, SCAN, BB, trec_X, trec_Y, tsys_X, tsys_Y)) %>%
  arrange(SCAN, ANTENNA, BB)

# Removed temp bad antennas from further analysis
if (nrow(atmant_bad) > 0) {
  atmclean <- 
    subset(atmclean,
           !as.character(ANTENNA) %in% as.character(atmant_bad$ANTENNA))
}

# Create summary 2, to detect mild outliers
atmsum2 <-
  atmclean %>%
  group_by(SCAN, BB) %>% 
  summarise(trX_min = boxplot.stats(trec_X, coef=2)$stat[1],
            trY_min = boxplot.stats(trec_Y, coef=2)$stat[1], 
            trX_max = boxplot.stats(trec_X, coef=2)$stat[5],
            trY_max = boxplot.stats(trec_Y, coef=2)$stat[5],
            tsX_min = boxplot.stats(tsys_X, coef=2)$stat[1],
            tsY_min = boxplot.stats(tsys_Y, coef=2)$stat[1], 
            tsX_max = boxplot.stats(tsys_X, coef=2)$stat[5],
            tsY_max = boxplot.stats(tsys_Y, coef=2)$stat[5])

# Detect atmosphere table warnings
atmclean <- left_join(atmclean, atmsum2, by=c('SCAN', 'BB'))

atmant_warn <-
  atmclean %>%
  subset(trec_X < trX_min | 
         trec_Y < trY_min | 
         tsys_X < tsX_min | 
         tsys_Y < tsY_min |
         trec_X > trX_max | 
         trec_Y > trY_max | 
         tsys_X > tsX_max | 
         tsys_Y > tsY_max )

atmclean$rn <- row.names(atmclean)


# Remove the ouliers for plotting and stat tables
if (nrow(atmant_warn) > 0) {
  atmant_warn$rn <- row.names(atmant_warn)
  atmclean <- 
    subset(atmclean,
           !rn %in% atmant_warn$rn)
}

# Final cleaned summary
atmsum1 <-
  atmclean %>%
  group_by(SCAN, BB) %>% 
  summarise(trecX = median(trec_X), trecY = median(trec_Y), 
            tsysX = median(tsys_X), tsysY = median(tsys_Y))

## We need to summarise atmosphere by using outgain, atmscan_bad, atmant_bad,
## atmant_warn
```

## Check Phase Calibrations.

```{r pha, warning=FALSE, echo=FALSE, message=FALSE, eval=FALSE}
# Remove Flagged

phase <- phase %>% subset(!as.character(ANT1) %in% antenna_flag | 
                            !as.character(ANT2) %in% antenna_flag)
phscan <- phase %>% group_by(SCAN) %>% summarise(scan = n())
phBB <- phase %>% group_by(BB) %>% summarise(scan = n())
phPOL <- phase %>% group_by(POL) %>% summarise(scan = n())

ch = 0
cha = 0
for (s in phscan$SCAN) {
  for (bb in phBB$BB) {
    for (pol in phPOL$POL) {
      phsbp <- subset(phase, SCAN == s & BB == bb & POL == pol)
      fit1 <- rqss(phsbp$PHASE_RMS~qss(phsbp$BLLENGTH, lambda=20),tau=0.05)
      fit2 <- rqss(phsbp$PHASE_RMS~qss(phsbp$BLLENGTH, lambda=20),tau=0.95)
      
      fita1 <- rqss(phsbp$AMP~qss(phsbp$BLLENGTH, lambda=20),tau=0.05)
      
      phf <- phsbp[(phsbp$PHASE_RMS < fitted(fit1)) | 
                     (phsbp$PHASE_RMS > fitted(fit2)), ]
      
      phfa <- phsbp[(phsbp$AMP < fitted(fita1)), ]
      
      a1 <- phf %>% group_by(ANT1) %>% summarise(flagged = n())
      a2 <- phf %>% group_by(ANT2) %>% summarise(flagged = n())
      
      aa1 <- phfa %>% group_by(ANT1) %>% summarise(flagged = n())
      aa2 <- phfa %>% group_by(ANT2) %>% summarise(flagged = n())
      
      names(a2)[1] <- 'ANT1'
      names(aa2)[1] <- 'ANT1'
      
      j <- full_join(a1, a2, by='ANT1')
      j[is.na(j$flagged.x), 'flagged.x'] <- 0
      j[is.na(j$flagged.y), 'flagged.y'] <- 0
      j$flag <- (j$flagged.x + j$flagged.y) / length(antennas$ANTENNA)
      j <- j[j$flag > 0.49,]
      
      if (nrow(j) > 0) {
        j$SCAN <- s
        j$BB <- bb
        j$POL <- pol
        if (ch == 0) {
          ph_flag <- j
          ch = 1
        } else {
          ph_flag <- bind_rows(ph_flag, j)
        }
      }
      
      j <- full_join(aa1, aa2, by='ANT1')
      j[is.na(j$flagged.x), 'flagged.x'] <- 0
      j[is.na(j$flagged.y), 'flagged.y'] <- 0
      j$flag <- (j$flagged.x + j$flagged.y) / length(antennas$ANTENNA)
      j <- j[j$flag > 0.49,]
      
      if (nrow(j) > 0) {
        j$SCAN <- s
        j$BB <- bb
        j$POL <- pol
        if (cha == 0) {
          pha_flag <- j
          cha = 1
        } else {
          pha_flag <- bind_rows(pha_flag, j)
        }
      }
    }
  }
}
```


```{r pha2, warning=FALSE, echo=FALSE, message=FALSE}
# Remove Flagged

phase <- phase %>% subset(!as.character(ANT1) %in% antenna_flag | 
                            !as.character(ANT2) %in% antenna_flag)
phscan <- phase %>% group_by(SCAN) %>% summarise(scan = n())
phBB <- phase %>% group_by(BB) %>% summarise(scan = n())
phPOL <- phase %>% group_by(POL) %>% summarise(scan = n())

ch = 0
for (s in phscan$SCAN) {
  for (bb in phBB$BB) {
    for (pol in phPOL$POL) {
      phsbp <- subset(phase, SCAN == s & BB == bb & POL == pol) %>% arrange(BLLENGTH)
      results <- locfit(phsbp$PHASE_RMS ~ lp(phsbp$BLLENGTH, h=30))
      
      sigmasqrhat = sum(residuals(results)^2) / 
        (nrow(phsbp) - 2 * as.numeric(results$dp[6]) + 
           as.numeric(results$dp[7]))
      
      critval = kappa0(results)$crit.val
      normell <- predict(results, where='data', what='vari')
      
      fit1 <- predict(results, phsbp) + 3 * critval*sqrt(sigmasqrhat*normell)
      fit2 <- predict(results, phsbp) - 3 * critval*sqrt(sigmasqrhat*normell)
      
#       plot(phsbp$BLLENGTH, phsbp$PHASE_RMS, cex=.2, ylim = c(0,120))
#       lines(phsbp$BLLENGTH, predict(results, phsbp))
#       lines(phsbp$BLLENGTH, fit1)
#       lines(phsbp$BLLENGTH, fit2)

      phf <- phsbp[(phsbp$PHASE_RMS < fit2) | 
                     (phsbp$PHASE_RMS > fit1), ]
      
      a1 <- phf %>% group_by(ANT1) %>% summarise(flagged = n())
      a2 <- phf %>% group_by(ANT2) %>% summarise(flagged = n())

      names(a2)[1] <- 'ANT1'
      
      j <- full_join(a1, a2, by='ANT1')
      j[is.na(j$flagged.x), 'flagged.x'] <- 0
      j[is.na(j$flagged.y), 'flagged.y'] <- 0
      j$flag <- (j$flagged.x + j$flagged.y) / length(antennas$ANTENNA)
      j <- j[j$flag > 0.65,]
      
      if (nrow(j) > 0) {
        j$SCAN <- s
        j$BB <- bb
        j$POL <- pol
        if (ch == 0) {
          ph_flag <- j
          ch = 1
        } else {
          ph_flag <- bind_rows(ph_flag, j)
        }
      }
    }
  }
}

```

## Check Pointing Calibrations.

```{r point, warning=FALSE, echo=FALSE, message=FALSE, results='asis'}
point <- point %>%
  subset(!as.character(ANTENNA) %in% antenna_flag)

point$off <- sqrt( point$REL_OFF_X ** 2 + point$REL_OFF_Y ** 2 )

posum <- point %>% 
  group_by(ANTENNA) %>% 
  summarise(rms = sd(off), limit = median(BW_X) / 10.) %>%
  subset(rms > limit)

point_trend <- point_trend %>%
  subset(!as.character(ANTENNA) %in% antenna_flag)

point_trend$off <- sqrt( point_trend$REL_OFF_X ** 2 + point_trend$REL_OFF_Y ** 2 )

trendsum <- point_trend %>% 
  group_by(ANTENNA) %>% 
  summarise(rms = sd(off), points = n()) %>%
  subset(rms > 2)

if (nrow(posum) > 0) {
  kable(posum, row.names = FALSE)
} else {
  cat("No Antennas with Pointing issues within the EB results")
}

if (nrow(trendsum) > 0) {
  kable(trendsum, row.names = FALSE)
} else {
  cat("No Antennas with Pointing issues within the last 10 hours.")
}


```


## Check Latest Focus.


## Check Latest Delay.

\pagebreak

# Pointing / Mosaic Details

```{r warning=FALSE, echo=FALSE, message=FALSE}
ggplot(aes(RA/15., DEC), data = fieldsrc) +
  geom_point(color = 'blue', size = 10, alpha = 0.3) +
  geom_point(aes(RA/15., DEC), data=subset(field, as.character(FIELD_NAME) %in% as.character(target_subscan$FIELD_NAME)))
```

\pagebreak

# Scans Information

```{r warning=FALSE, echo=FALSE, message=FALSE}
kable(
  select(scan, SCAN, NUM_SUBSCAN, START_TIME, END_TIME, SCAN_INTENT, 
         FIELD_NAME),
  col.names = c('Scan', 'SubSc.', 'Start', 'End', 'Intent', 'Field'))
```

\pagebreak

# Atmosphere Details

```{r warning=FALSE, echo=FALSE, message=FALSE}
# kable(outgain, row.names = F)

kable(atmsum1, row.names = F)

if (nrow(outgain) > 0) {
  kable(outgain, row.names = F)
}

if (nrow(atmscan_bad) > 0) {
  kable(atmscan_bad, row.names = F)
}

if (nrow(atmant_bad) > 0) {
  kable(atmant_bad, row.names = F)
}

if (nrow(atmant_warn) > 0) {
  warn_sum <- 
    select(atmant_warn, SCAN, ANTENNA, BB, trec_X, trec_Y, tsys_X, tsys_Y) %>% 
    group_by(ANTENNA, BB) %>% 
    summarise(Scans = n())
  kable(arrange(warn_sum, ANTENNA), row.names = F)
}


```

```{r dpi=180, fig.height=9, warning=FALSE, echo=FALSE, message=FALSE}
p1 <- ggplot(aes(factor(SCAN), trec_X), data=atmclean) + 
  geom_point(aes(color=ANTENNA), position=position_jitter(w=0.1, h=0)) + 
  geom_boxplot(coef=2) + 
  facet_wrap( ~ BB, ncol=1) + 
  xlab('SCAN #') + ylab('TRec, Pol. X') + 
  guides(color=FALSE)

p2 <- ggplot(aes(factor(SCAN), trec_Y), data=atmclean) +  
  geom_point(aes(color=ANTENNA), position=position_jitter(w=0.1, h=0)) + 
  geom_boxplot(coef=2) + 
  facet_wrap( ~ BB, ncol=1) + 
  xlab('SCAN #') + ylab('TRec, Pol. Y') + 
  guides(color=FALSE)

grid.arrange(p1, p2, ncol = 2)
```

```{r dpi=180, fig.height=9, echo=F, message=FALSE, warning=FALSE}
p1 <- ggplot(aes(factor(SCAN), tsys_X), data=atmclean) + 
  geom_point(aes(color=ANTENNA), position=position_jitter(w=0.1, h=0)) + 
  geom_boxplot(coef=2) + 
  facet_wrap( ~ BB, ncol=1) + 
  xlab('SCAN #') + ylab('TSys, Pol. X') + 
  guides(color=FALSE)

p2 <- ggplot(aes(factor(SCAN), tsys_Y), data=atmclean) +  
  geom_point(aes(color=ANTENNA), position=position_jitter(w=0.1, h=0)) + 
  geom_boxplot(coef=2) + 
  facet_wrap( ~ BB, ncol=1) + 
  xlab('SCAN #') + ylab('TSys, Pol. Y') + 
  guides(color=FALSE)

grid.arrange(p1, p2, ncol = 2)

# fit1 <- rqss(phsel$PHASE_RMS~qss(phsel$BLLENGTH, lambda=20),tau=0.05)
# fit2 <- rqss(phsel$PHASE_RMS~qss(phsel$BLLENGTH, lambda=20),tau=0.9)
```

\pagebreak

# Delay

```{r fig.height=9, warning=FALSE, echo=FALSE, message=FALSE}

delay_uid <- 
  subset(delay, 
         BAND == as.character(sbsum[1, 'band']) & 
           as.character(ANTENNA) %in% antennas$ANTENNA)

if (nrow(delay_uid) > 0) {
  p1 <- ggplot(aes(as.factor(TIME), delay_X * 1E9), data = delay_uid) + 
    geom_point(aes(color = ANTENNA)) + 
    geom_hline(yintercept = c(0.25, 0, -0.25), linetype = c(2,1,2)) +
    facet_wrap( ~ BB, ncol=1) +
    guides(color=F)
  
  p2 <- ggplot(aes(as.factor(TIME), delay_Y * 1E9), data = delay_uid) + 
    geom_point(aes(color = ANTENNA)) + 
    geom_hline(yintercept = c(0.25, 0, -0.25), linetype = c(2,1,2)) +
    facet_wrap( ~ BB, ncol=1) +
    guides(color=F)

  grid.arrange(p1, p2, ncol = 2)
} else {
  cat("No delays Observations with this band in the last 6 hours.\n")
}

```

\pagebreak

# Phase
```{r warning=FALSE, echo=FALSE, message=FALSE}
if (ch == 1) {
  kable(ph_flag,
        caption = "Antennas with Phase Issues")
}
```


```{r fig.height=9, warning=FALSE, echo=FALSE, message=FALSE}
for (i in phscan$SCAN) {
  phsel <- subset(phase, SCAN == i)    
  blph <- ggplot(aes(BLLENGTH, PHASE_RMS), data = phsel) + 
    geom_point(alpha=0.3) + 
    stat_quantile(
      method = 'rqss',
      formula = y ~ qss(x, lambda = 25, constraint="N"), quantiles = c(0.05, 0.95)) +
    coord_cartesian(ylim = c(0,120)) +
    facet_grid(BB ~ POL) +
    ggtitle(as.character(i))
  print(blph)
  
  cat('\r\n\r\n')
}
```
